### 2023-09-21 thesis/MSECE_thesis.tex
More spelling corrections, thesis section on spelling errors and inconsistencies in transcripts.

\usepackage{cite}
\usepackage{listings}
\usepackage{multicol}
\usepackage{newtxtext}
\usepackage{setspace}
\usepackage{sectsty}
\usepackage{booktabs}
\usepackage[numbib]{tocbibind}
\usepackage[lmargin=1.25in,rmargin=1.25in,tmargin=1.0in,bmargin=1.0in]{geometry}

@@

\section{Data Processing}\label{sec:data_processing}
All of the corpora listed above (see~\ref{sec:data_source}) are created at different times, for different purposes, and by different authors.
As a result, the data in these corpora all have different formats and need to be processed into a common format to be used together, with the goal
being to essentially create a super-corpus that includes all the corpora listed above.

All data was processed in Python using primarily built-in functions/modules\footnote{The \lstinline|re| and \lstinline|xml| modules were also used although
    these are built into most Python distributions by default.}. The text data is extracted from the corpus transcripts i.e.~Lisp in ATCC, XML in
ATCO2 and ZCU CZ ATC, and plain text in ATCOSIM, the transcriber annotations are removed where necessary\footnote{A copy of the original data is
    made, then the annotations are removed from the copy.}, and the resulting text is written in the standard corpus format (an ASCII text file with
one line in the file corresponding to one sample from the corpus) to a file.

@@

Sci-Kit Learn's implementation of the LOF
algorithm\footnote{https://scikit-learn.org/stable/modules/generated/sklearn.neighbors.LocalOutlierFactor.html\#sklearn-neighbors-localoutlierfactor}
was used with a value of \(N = 35\) for \(N\) neighbors in the K-Nearest Neighbors algorithm and Minkowski distance for distance metrics/calculations
(in this case, since \(p=2\), Euclidean distance is effectively used for distance calculations). A total of 47 samples were detected as outliers and
removed for analysis and are summarized in table \ref{}

\begin{table}[h!]
    \centering
    \begin{tabular}{l | r}
        \toprule
        \multicolumn{2}{c}{Outlier Properties}   \\
        \midrule
        \textbf{Mean Sequence Length}    & 47.30 \\
        \textbf{Std of Sequence Length}  & 11.82 \\
        \textbf{Minimum Sequence Length} & 38    \\
        \textbf{Maximum Sequence Length} & 73    \\
        \textbf{\# Samples}              & 47    \\
        \bottomrule
    \end{tabular}
    \label{table:outlier_stats}
    \caption{}
\end{table}

>>>>

\usepackage{cite}
\usepackage{listings}
\usepackage{multicol}
\usepackage{newtxtext}
\usepackage{setspace}
\usepackage{sectsty}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[numbib]{tocbibind}
\usepackage[lmargin=1.25in,rmargin=1.25in,tmargin=1.0in,bmargin=1.0in]{geometry}

@@

\section{Data Processing}\label{sec:data_processing}
All of the corpora listed above (see~\ref{sec:data_source}) are created at different times, for different purposes, and by different authors.
As a result, the data in these corpora all have different formats and need to be processed into a common format to be used together, with the goal
being to essentially create a ``super-corpus'' that includes all the corpora listed above (i.e., a superset of the other corpora).

All data was processed in Python using primarily built-in functions/modules\footnote{The \lstinline|re| and \lstinline|xml| modules were also used
    although these are built into most Python distributions by default.}. The text data is extracted from the corpus transcripts parsing from the
corpora-specific formats where necessary i.e.~Lisp in ATCC, XML in ATCO2 and ZCU CZ ATC, and plain text in ATCOSIM, the transcriber annotations
are removed where necessary\footnote{A copy of the original data is made, then the annotations are removed from the copy.}, and the resulting text
is written to a file in the standard corpus format (an ASCII text file with one line in the file corresponding to one sample from the corpus) to a
file.

\subsection{Handling Spelling Errors \& Inconsistencies}\label{sec:spelling_errors}
By the nature of the data labeling process, there are bound to be spelling errors introduced by the annotators during corpora creation. This gets
exacerbated by the aggregation of several corpora with varying controls for correcting spelling errors and inconsistencies. Nearly all of the errors
are recoverable/correctable given context. For example, ``possibility of \textbf{tornado's}'' should clearly have been
``possibility of \textbf{tornadoes}'', changing the posessive form of ``tornado'' to the plural form. There are also instances of spelling conventions
that are consistent within corpora, but become inconsistent when the corpora are combined.

% 22 spelling errors
Manually reviewing every sample in the corpus is unrealistic considering that there are over 50,000 data samples and would be subject the same
human error that introduced those errors in the first place. Instead, the frequency of occurence of tokens in the corpora combined with manual review
thereafter, was used to detect and correct the most common errors. Tokens with the lowest frequency across corpora were manually reviewed and
corrected where necessary. An \(A \rightarrow B\) mapping system was used to correct the errors, where \(A\) is the erroneous token and \(B\) is the
corrected or replaced token. A total of 22 unique errors were detected and subsequently corrected or removed using this method.

% hesitations, cut off words, different kinds of filled pauses
The mapping system described above is also used to modify within corpora conventions to be consistent across corpora. Three areas are addressed here:
hesitations, cut-off or partial words, and filled pauses within speech. These areas are defined differently between the four corpora, which makes
unifying the transcripts difficult. Hesitations, for example, are defined by one corpus as any incomplete or non-english speech sounds and left
completely undefined by another (despite annotators making notes about hesitations). The way in which hesitations, pauses, and partial words are
transcribed differs between corpora as well. Two corpora prescribe special tokens to these phenomena such as ``[hes]'', ``[hesitation]'', ``<pause>'',
or similar, while the others transcribe the data as it sounds (i.e., ``uh'', ``eh'', or ``er'' for filled pauses and ``cir-'' or ``cir+'' for
instances that were cut-off mid pronunciation). In order to facilitate the unification of the transcripts for all four copora, all three of these
phenomena have been redefined with accompanying translation/replacement rules below:

@@

Sci-Kit Learn's implementation of the LOF
algorithm\footnote{https://scikit-learn.org/stable/modules/generated/sklearn.neighbors.LocalOutlierFactor.html\#sklearn-neighbors-localoutlierfactor}
was used with a value of \(N = 35\) for \(N\) neighbors in the K-Nearest Neighbors algorithm and Minkowski distance for distance metrics/calculations
(in this case, since \(p=2\), Euclidean distance is effectively used for distance calculations). A total of 47 samples were detected as outliers and
removed for analysis and are summarized in table~\ref{table:outlier_stats}.

\begin{table}[h!]
    \centering
    \begin{tabular}{l | r}
        \toprule
        \multicolumn{2}{c}{Outlier Properties}   \\
        \midrule
        \textbf{Mean Sequence Length}    & 47.30 \\
        \textbf{Std of Sequence Length}  & 11.82 \\
        \textbf{Minimum Sequence Length} & 38    \\
        \textbf{Maximum Sequence Length} & 73    \\
        \textbf{\# Samples}              & 47    \\
        \bottomrule
    \end{tabular}
    \label{table:outlier_stats}
    \caption{Mean, standard deviation, minimum, and maximum sequence length of samples detected as outliers.}
\end{table}

Although all of the outliers have higher sequence lengths than the typical sequence lengths of the other samples in the data, going the through
the outlying samples manually and reviewing each reveals that, for the most part, the samples are typical albeit somewhat complex communications.
With the exception of four outliers, all of the samples labeled as outlying by the LOF algorithm were kept in the data.
